---
title: "AG_Bio720_Dec5_Assignment"
author: "Amelia Guo"
date: '2018-12-05'
output:
  html_document: default
  pdf_document: default
---
#Question 1: 
DataCamp chapters on "Introduction to Bioconductor" have been completed.

#Question 2: 
This is the simulator I have written for diploids. In this function, I have placed in arguments that allows us to try different initial allele frequencies (p0), fitness of each genotype (wAA, wAa, waa), and number of generations (n).

The followig function can report whether the beneficial allele fixes by the end of the simulation. 
```{r echo=TRUE}
diploid_selection <- function(p0 = 0.01, wAA = 1, wAa = 0.9, waa = 0.3, n = 100) {
    
    # Initialize vectors to store allele frequencies and mean pop fitness
    p <- rep(NA,n)  # a vector to store allele frequencies
    
    w_bar <- rep(NA, n)
     
    # starting conditions
   	p[1] <- p0 # starting allele frequencies
	  w_bar[1] <- (p[1]^2*wAA) + (2*p[1]*(1-p[1])*wAa) + ((1-p[1])^2*waa)
	
	# now we need to loop from generation to generation
	for ( i in 2:n) {
		w_bar[i - 1] <- (p[i - 1]^2*wAA) + (2*p[i - 1]*(1-p[i - 1])*wAa) + ((1-p[i - 1])^2*waa) # mean population fitness
		p[i] <- (p[i - 1]^2*(wAA/w_bar[i - 1])) + (p[i - 1]*(1-p[i - 1])*(wAa/w_bar[i - 1]))
	}
    
    return(p)
}

diploid_selection(p0 = 0.01, wAA = 1, wAa = 0.9, waa = 0.3, n = 100)

```


The follwing can plot the trajectory of the beneficial allel across generations. 
```{r echo=TRUE}
d <- diploid_selection()
generations <- 1:length(d)
plot(d ~ generations, pch = 20, 
     ylab = "allele frequency", 
     xlab = "generation")
```


#Question 3: 
The following function is my genetic drift simulator, with the arguments including the number of alleles (size), the starting allele frequency (p0a and p0A), and the number of generations (n). 

```{r}

genetic_drift <- function(pop = 40, p0a = 0.5, p0A = 0.5, n = 100) {

allele_counts <- sample(c("a", "A"),
                        size = pop, 
                        replace = TRUE,
                        prob = c(p0a,p0A))
allele_freq <- table(allele_counts)/length(allele_counts)

for (i in 2:n) {
  
  if( i == 1){
    c <- sample(c("a", "A"),
                        size = pop, 
                        replace = TRUE,
                        prob = allele_freq)
    f <- table(allele_counts)/length(allele_counts)
    
    allele_counts<-rbind(allele_counts,c)
    allele_freq<-rbind(allele_freq,f)
  } else {
     c <- sample(c("a", "A"),
                        size = pop, 
                        replace = TRUE,
                        prob = allele_freq[i,])
    f <- table(allele_counts[i,])/length(allele_counts[i,])
    
    allele_counts<-rbind(allele_counts,c)
    allele_freq<-rbind(allele_freq,f)
  }


  }
}
```

#Question 4: 
```{r}
sim <- replicate(n = 1000, genetic_drift(n = 100, p0a = 0.5, p0A = 0.5, pop = 400))
```

#Question 5:
```{r}
plot(frequency ~ generations, pch = 20, cex = 1.5)
matlines(x = generations[,1], y = frequency()[,1:100], lwd=c(3,3,3), lty=c(1,2,2), col = 1)
```

#Question 6: 
Re-wrote this as a function: 
```{r echo=TRUE}
stat <- function(obs = 20, intercept = 0.5, slope = 0.1, error = 0) {
x <- seq(from = 1, to = 10, length.out = obs) # length.out is how many observations we will have 
a <- intercept # intercept
b <- slope # slope
y_deterministic <- a + b*x
y_simulated <- rnorm(length(x), mean = y_deterministic, sd = 0)
mod_sim <- lm(y_simulated ~ x)
p_val_slope <- summary(mod_sim)$coef[2,4] # extracts the p-value p_val_slope
p_val_slope 
}
```

I know that this function works because if we change the sd error to 0, then we should get the same answer, which we do. 
```{r echo=TRUE}
x <- seq(from =1, to = 10, length.out = 20) # length.out is how many observations we will have 
a <- 0.5 # intercept
b <- 0.1 # slope
y_deterministic <- a + b*x
y_simulated <- rnorm(length(x), mean = y_deterministic, sd = 0)
mod_sim <- lm(y_simulated ~ x)
p_val_slope <- summary(mod_sim)$coef[2,4] # extracts the p-value p_val_slope
p_val_slope
```

```{r echo=TRUE}
rep <- replicate(n = 1000, stat(error = 20))

hist(rep, freq = T, breaks = 20)
```
The histogram above shows me that the p value was less than 0.5 in approimately 50 out of 1000 times. 

```{r echo=TRUE}
rep2 <- replicate(n = 1000, stat(slope = 0, error = 20))

hist(rep2, freq = T, breaks = 20)
```
This didn't change the frequence of p values less than 0.5 much. The frequencies is already 40-50 every time. 


